\section{Databases}\label{sec:databases}

\subsection{RDS}\label{subsec:rds}
Relational Database Service (RDS) is a \textbf{managed DB service} that handles: PostgreSQL, MySQL, MariaDB, Oracle, Microsoft SQL Server, Aurora (AWS proprietary database).
It's great for OLTP (On-Line Transaction Processing).

\subsubsection{Aurora:}
Cloud Optimized DB (5x better) and compatible with PostgreSQL and MySQL, but it's more expensive (20\% more).
It automatically grows in increments of 10GB (up to 64TB).

\subsection{ElastiCache}\label{subsec:elasticache}
Managed Redis or Memcached databases. \textbf{In-memory key-value databases} with high performance.
Great for  caching Real heavy queries.

\subsection{DynamoDB}\label{subsec:dynamodb}
\textbf{Fully Managed, serverless}, key-value, high-available (replication 3 AZ) database with \textbf{single, digit millisecond latency}\@.

\subsection{Redshift}\label{subsec:redshift}
\textbf{Columnar} database, based on PostgreSQL and has a SQL interface for performing queries.
It's great for  OLAP (On-Line Analytical Processing).

\subsection{EMR}\label{subsec:emr}
Elastic Map Reduce helps you create a \textbf{Hadoop cluster}\@.
It supports Apache Spark, HBase, Presto, Flink \ldots It's great for data processing, machine learning, indexing websites, big data\ldots

\subsection{Athena}\label{subsec:athena}
Fully \textbf{query engine} with \textbf{SQL capabilities}\@.
It is used to query data in S3.

\subsection{DMS}\label{subsec:dms}
Database Migration Service (DMS), quickly and securely \textbf{migrates databases to AWS}\@.

\subsection{Glue}\label{subsec:glue}
Is a \textbf{fully serverless} \textbf{ETL (Extract Transform Load)} service.
